Figures to insert in text

### 2018-02-28 Chapters/sdm-applications.tex
SDM TicTacToe board sequence
Improve TicTacToe board sequence

\section{Results (iv): Supervised classification application}

@@

\section{Results (iii): Supervised image noise filtering application}

@@

\section{Results (v): The possibility of unsupervised reinforcement learning}

@@

After a game has finished, it is time to learn from its decisions. Thus, if SDM wins the game, it will write the whole sequence of boards to SDM. Let $b_0, b_1, b_2, \dots, b_n$ be the board sequence of the game. Then it will write $b_0 \rightarrow b_1 \rightarrow b_2 \rightarrow \cdots \rightarrow b_n$, with possibly different weights for each transition. If it loses, it will reverse the board (replace X by O and vice versa), and will act as if it had won. Hence, it will learn which sequences lead to victory. When a new board appears, it may have already seen that situation and will decide according to the sequences which goes towards victory. This is our positive reward learning.

>>>>

\chapter{Results (iv): Supervised classification application}

@@

\chapter{Results (iii): Supervised image noise filtering application}

@@

\chapter{Results (v): The possibility of unsupervised reinforcement learning}

@@

After a game has finished, it is time to learn from its decisions. Thus, if SDM wins the game, it will write the whole sequence of boards to SDM. Let $b_0, b_1, b_2, \dots, b_n$ be the board sequence of the game (see Figure \ref{fig-ttt-example}). Then it will write $b_0 \rightarrow b_1 \rightarrow b_2 \rightarrow \cdots \rightarrow b_n$, with possibly different weights for each transition. If it loses, it will reverse the board (replace X by O and vice versa), and will act as if it had won. Hence, it will learn which sequences lead to victory. When a new board appears, it may have already seen that situation and will decide according to the sequences which goes towards victory. This is our positive reward learning.

\begin{figure}
    \captionsetup[subfigure]{labelformat=empty}
    %\centering

    \subfloat[$b0$]{\begin{tabular}{p{\widthof{x}}|p{\widthof{x}}|p{\widthof{x}}}
     & & \\\hline  & & \\\hline  & &
    \end{tabular}}
    {$\xrightarrow{w_0}$}
    \subfloat[$b1$]{\begin{tabular}{p{\widthof{x}}|p{\widthof{x}}|p{\widthof{x}}}
     & & \\\hline  &x& \\\hline  & &
    \end{tabular}}
    {$\xrightarrow{w_1}$}
    \subfloat[$b2$]{\begin{tabular}{p{\widthof{x}}|p{\widthof{x}}|p{\widthof{x}}}
     & & \\\hline o&x& \\\hline  & &
    \end{tabular}}
    {$\xrightarrow{w_2}$}
    \subfloat[$b3$]{\begin{tabular}{p{\widthof{x}}|p{\widthof{x}}|p{\widthof{x}}}
    x& & \\\hline o&x& \\\hline  & &
    \end{tabular}}
    {$\xrightarrow{w_3}$}
    \subfloat[$b4$]{\begin{tabular}{p{\widthof{x}}|p{\widthof{x}}|p{\widthof{x}}}
    x& & \\\hline o&x& \\\hline  & &o
    \end{tabular}}
    {$\xrightarrow{w_4}$}
    \subfloat[$b5$]{\begin{tabular}{p{\widthof{x}}|p{\widthof{x}}|p{\widthof{x}}}
    x&x& \\\hline o&x& \\\hline  & &o
    \end{tabular}}
    {$\xrightarrow{w_5}$}
    \subfloat[$b6$]{\begin{tabular}{p{\widthof{x}}|p{\widthof{x}}|p{\widthof{x}}}
    x&x&o\\\hline o&x& \\\hline  & &o
    \end{tabular}}
    {$\xrightarrow{w_6}$}
    \subfloat[$b7$]{\begin{tabular}{p{\widthof{x}}|p{\widthof{x}}|p{\widthof{x}}}
    x&x&o\\\hline o&x& \\\hline  &x&o
    \end{tabular}}

    \caption{Example of a game with 7 movements in which X wins.\label{fig-ttt-example}}
\end{figure}
